MSA Asthma Place of Service Timeseries

### 2018-06-08 r_scripts/analysis/msa_asthma_timeseries.Rmd
Couldn't figure out overlap.

```{r save_df}
# write asthma weekly count
#write_csv(asthma_weekly_count, './data/health/asthma_weekly_count.csv')
# write pm msa
#write_csv(msa_pm, './data/pm/msa_pm.csv')
```

>>>>

```{r save_df, eval=F}
# write asthma weekly count
#write_csv(asthma_weekly_count, './data/health/asthma_weekly_count.csv')
# write pm msa
#write_csv(msa_pm, './data/pm/msa_pm.csv')
```

Overlap plot.

```{r eval=F}
grid::grid.newpage()
vp1 <- grid::viewport(width = 1, height = 1, x = 0.5, y = 0.5)
vp2 <- grid::viewport(width = 1, height = 1, x = 0.5, y = 0.5)
print(pm_msa_plot, vp = vp1)
print(pos_plot, vp = vp2)
```
